---
title: "station_download"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{station_download}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r init, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The waterDataSupport package is intended to simplify normally complex tasks
associated with collecting data.

Because the goal of the package is simplicity, it is intended to be less robust
than the original code on which it is based.


```{r setup}
library(waterDataSupport)
```

The as.International.Date() function has only one input which is a date in 
international format.  International format (YY/mm/dd) is recommended to avoid 
confusion with other formats.

```{r stations}

BEGIN_DATE = as.International.Date("1992/1/1")
END_DATE = as.International.Date("2022/12/1")


```


The Select_NOAA_Stations function downloads selected stations from NOAA

If a message concerning cached files show up, check the date to ensure it is 
recent.

```{r stations}


VARS_NOAA <- c("PRCP", "TMAX", "TMIN")

stations <- Select_NOAA_Stations(refresh = FALSE,
                                 selectElements = VARS_NOAA,
                                 beginYear = as.Year(BEGIN_DATE),
                                 endYear = as.Year(END_DATE))
```

```{r unique_stations}


VARS_NOAA <- c("PRCP", "TMAX", "TMIN")

stations <- Select_NOAA_Stations(refresh = FALSE,
                                 selectElements = VARS_NOAA,
                                 beginYear = as.Year(BEGIN_DATE),
                                 endYear = as.Year(END_DATE),
                                 unique_stations = TRUE)

```





